Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\textbf{25. Reviewer's Comment:}
Page 9, first full paragraph, first sentence: replace “hypotheses state” with
“hypotheses posit”.

\textbf{25. Response:}

\begin{quote}
\color{blue}
We replaced the word ``state'' according to the reviewer's suggestion.
\end{quote}

\textbf{26. Reviewer's Comment:}
Page 9, Danaini subsection: Remove the sentence beginning “Among them is for
example...” and just mention the Monarch at the end of the preceding sentence:
“...involved in mimicry rings, including the best-known migratory butterfly,
the monarch (Danaus plexippus).”

\textbf{26. Response:}

\textbf{27. Reviewer's Comment:}
Page 9, Danaini subsection: Revise or remove the last sentence of this 
paragraph. It is not immediately clear what the age of a species has to do 
with genetic diversity and speciation (or even what the age of a species 
really is...).

\textbf{27. Response:}

\begin{quote}
\color{blue}
We reworded the sentence according to the reviewer's suggestion:

``It has been found
in highly vagile species in the nymphalid genus \emph{Vanessa} that
dispersal has homogenized populations due to gene flow, as 
vagile species seem to be genetically homogeneous in their
populations Wahlberg N, Rubinoff D (2011).''
\end{quote}

### 2015-01-14 MS_revised.tex
comment 27

\subsubsection*{Danaini}
Our MultiMEDUSA approach showed a significant slowdown in net
diversification rate in the subtribe Danaina of the Danini. Both Danaina
and the sister clade Euploeina feed mainly on Apocynaceae and thus a
hostplant shift should not be responsible for the observed slowdown of
diversification in the Danaina. As expected, our BiSSE analysis of
Apocynaceae feeders shows that there is no effect of feeding on this
plant family on the net diversification rates of Nymphalidae lineages.
Many of the Danaina are large, strong fliers, highly migratory and
involved in mimicry rings, including the best-known migratory butterfly,
the monarch (\emph{Danaus plexippus}).
The causes for a lower net diversification rate in the
Danaina remains to be investigated, but their great dispersal power
might be involved in preventing allopatric speciation. It has been found
in highly vagile species in the nymphalid genus \emph{Vanessa} that
dispersal has homogenized populations due to gene flow, as old and
vagile species seem to be genetically homogeneous while younger
widespread species show higher genetic differentiation in their
populations \cite{wahlberg2011}.

>>>>

\subsubsection*{Danaini}
Our MultiMEDUSA approach showed a significant slowdown in net
diversification rate in the subtribe Danaina of the Danini. Both Danaina
and the sister clade Euploeina feed mainly on Apocynaceae and thus a
hostplant shift should not be responsible for the observed slowdown of
diversification in the Danaina. As expected, our BiSSE analysis of
Apocynaceae feeders shows that there is no effect of feeding on this
plant family on the net diversification rates of Nymphalidae lineages.
Many of the Danaina are large, strong fliers, highly migratory and
involved in mimicry rings, including the best-known migratory butterfly,
the monarch (\emph{Danaus plexippus}).
The causes for a lower net diversification rate in the
Danaina remains to be investigated, but their great dispersal power
might be involved in preventing allopatric speciation. It has been found
in highly vagile species in the nymphalid genus \emph{Vanessa} that
dispersal has homogenized populations due to gene flow, as 
vagile species seem to be genetically homogeneous in their
populations \cite{wahlberg2011}.
